Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-19 2015-turklang-kazdep/paper.tex
more
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60846 72bbbca6-d526-0410-a7d9-f06f51895060
header fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60847 72bbbca6-d526-0410-a7d9-f06f51895060
beginnings of background
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60849 72bbbca6-d526-0410-a7d9-f06f51895060

\title{Towards a free/open-source universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA\footnote{Corresponding author.  E-mail address: jonwashi@indiana.edu}}

@@

\maketitleabstract{}

@@

% case and function
% "zero" derivation

@@

\bibliographystyle{apa}
\bibliography{paper}

>>>>

\title{Towards a free/open-source universal-dependency treebank for Kazakh}
\name{Francis M. Tyers$^a$ and Jonathan Washington$^b$}
\shortauthor{Tyers \& Washington}
\address{$^a$ HSL-fakultehta, UiT Norgga árktalaš universitehta, N-9015 Tromsø, Norway\\
	$^b$ Departments of Linguistics and Central Eurasian Studies, Indiana University, Bloomington, IN 47405, USA\footnote{Corresponding author.  E-mail address: jonwashi@indiana.edu}}

@@

\maketitleabstract{}
\thispagestyle{firststyle}

@@

Kazakh (қазақ тілі), a Turkic language of Central Asia with around 12 million speakers, hargle bargle. %FIXME

In the process of designing a Kazakh transducer \citep{Washington14}, several decisions were made about how various inflectional morphemes affect the part of speech and syntactic function of various word forms.  These decisions include the relations to other words defined by ``case'' morphemes, and processes of ``zero derivation''.

% case and function
%% indefinite acc/gen = "nom"
%% attr/subst/advl function of cases
% "zero" derivation
%% attr/subst/etc.
%% copulas?

@@

\bibliographystyle{apalike}
\bibliography{paper}
